Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa

### 2023-03-09 src/docs_paper/paper.Rmd
Two typos (maybe the last ones?)

\begin{table}[htb]
\small
\centering
\begin{tabularx}{\textwidth}{lp{6cm}ll}
\toprule
Risk group & Description & Local HIV & Incidence ratio \\
 & & incidence & \\
\midrule
None & Not sexually active & -- & 0.0 \\
Low & One cohabiting partner & -- & 1.0 (Baseline) \\
High & Non-regular or multiple partner(s) & -- & 1.72 \\
 & & $<$0.1\% & 25.0 \\
 & & 0.1-0.3\% & 13.0 \\
 Very high & Transactional sex (adjusted to correspond & 0.3-1.0\% & 9.0 \\
 & to female sex workers) & 1.0-3.0\% & 6.0 \\
 & & $>$3.0\% & 3.0 \\
\bottomrule
\end{tabularx}
\caption{HIV risk groups and assumed HIV incidence rate ratio for each risk group relative to AGYW with one cohabiting sexual partner. Among FSW, the incidence rate ratio depended on the level of HIV incidence among the general population. The incidence rate ratio for women with non-regular or multiple sexual partner(s) was derived from analysis of ALPHA network data. Non-regular partners are defined to be non cohabiting. The transactional sex risk group is adjusted during analysis to correspond to female sex worker, and incidence rate ratios among FSW were dervied based on patterns of relative HIV prevalence among FSW compared to general population prevalence. When the local HIV incidence in the general population is higher, the incidence rate ratio for FSW is lower.}
\label{tab:risk-groups}
\small
\end{table}

@@

```{r within-between-country-variation, fig.cap="National (in white) and subnational (in color) posterior means of the risk group proportions. Estimates are stratified by risk group (columns) and five-year age group (rows). Regions of sub-Saharan Africa were defined according to the UN M49 geocode [@un2020statistics]. \\label{fig:within-between-country-variation}"}
knitr::include_graphics("depends/3p1-within-between-country-variation.png")
```

>>>>

\begin{table}[htb]
\small
\centering
\begin{tabularx}{\textwidth}{lp{6cm}ll}
\toprule
Risk group & Description & Local HIV & Incidence ratio \\
 & & incidence & \\
\midrule
None & Not sexually active & -- & 0.0 \\
Low & One cohabiting partner & -- & 1.0 (Baseline) \\
High & Non-regular or multiple partner(s) & -- & 1.72 \\
 & & $<$0.1\% & 25.0 \\
 & & 0.1-0.3\% & 13.0 \\
 Very high & Transactional sex (adjusted to correspond & 0.3-1.0\% & 9.0 \\
 & to female sex workers) & 1.0-3.0\% & 6.0 \\
 & & $>$3.0\% & 3.0 \\
\bottomrule
\end{tabularx}
\caption{HIV risk groups and assumed HIV incidence rate ratio for each risk group relative to AGYW with one cohabiting sexual partner. Among FSW, the incidence rate ratio depended on the level of HIV incidence among the general population. The incidence rate ratio for women with non-regular or multiple sexual partner(s) was derived from analysis of ALPHA network data. Non-regular partners are defined to be non cohabiting. The transactional sex risk group is adjusted during analysis to correspond to female sex worker, and incidence rate ratios among FSW were derived based on patterns of relative HIV prevalence among FSW compared to general population prevalence. When the local HIV incidence in the general population is higher, the incidence rate ratio for FSW is lower.}
\label{tab:risk-groups}
\small
\end{table}

@@

```{r within-between-country-variation, fig.cap="National (in white) and subnational (in color) posterior means of the risk group proportions. Estimates are stratified by risk group (columns) and five-year age group (rows). \\label{fig:within-between-country-variation}"}
knitr::include_graphics("depends/3p1-within-between-country-variation.png")
```
